---
title: "Data Visualization Homework 2"
author: "Olivia Wilson-Pietrzak"
editor: visual
format:
  html:
    code-fold: true
    code-summary: "Show code"
    code-tools: true
---

### Question 1

You can change the pch in the plot command. [Pch stands for plot character, and there are over 250 options (1-25 are standard vector and R symbols).](https://r-charts.com/base-r/pch-symbols/) You can also change the color and size of the pch points using the col, bg, and cex commands (see below).

The numbers in front of the graph title change the location of the graph title within the box. The command will not display text outside of the graph box.

```{r}
plot(pressure, pch = 5)  # Can you change pch?
plot(pressure, pch = 25, bg = "pink", col = "blue", cex = 3)

text(150, 600, 
     "Pressure (mm Hg)\nversus\nTemperature (Celsius)")
```

### Question 2

```{r}
# Setting the parameter (3 rows by 2 cols)
par(mfrow=c(3, 2))

# Scatterplot
# Note the incremental additions

x <- c(0.5, 2, 4, 8, 12, 16)
y1 <- c(1, 1.3, 1.9, 3.4, 3.9, 4.8)
y2 <- c(4, .8, .5, .45, .4, .3)

# Setting label orientation, margins c(bottom, left, top, right) & text size
par(las=1, mar=c(4, 4, 2, 4), cex=.7) 
plot.new()
plot.window(range(x), c(0, 6))
lines(x, y1)
lines(x, y2)
points(x, y1, pch=16, cex=2) # Try different cex value?  
points(x, y2, pch=21, bg="white", cex=2)  # Different background color
par(col="gray50", fg="gray50", col.axis="gray50")
axis(1, at=seq(0, 16, 4)) # What is the first number standing for?
axis(2, at=seq(0, 6, 2))
axis(4, at=seq(0, 6, 2))
box(bty="u")
mtext("Travel Time (s)", side=1, line=2, cex=0.8)
mtext("Responses per Travel", side=2, line=2, las=0, cex=0.8)
mtext("Responses per Second", side=4, line=2, las=0, cex=0.8)
text(4, 5, "Bird 131")
par(mar=c(5.1, 4.1, 4.1, 2.1), col="black", fg="black", col.axis="black")

```

```{r}

```
